---
title: "Project Proposal"
author: "Brandon Parmanand"
date: '2022-06-27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Clear workspace.
rm(list=ls(all=TRUE))

# Set Working Directory
wdpath <- ("~/GitHub/Parmanand STA5104 Project")
setwd(wdpath)

# Intall needed libraries
library(tidyverse) 
library(ggplot2) 
library(GGally)


#Read in Data 
Movies.df <- read_csv("movies.csv")
```
# Data Description

The dataset contains 651 instances of movies released in theaters between the period of 1970 -- 2014. The variables of the data set include IMBD ratings, rotten tomatoes critics and audience ratings and scores, actors and directors, movie runtime, genre, releases dates, award nominations and wins, and more. Some variables will be deleted as it has no value to my intended statistical analysis such as the list of actors.

```{r}
# Do some initial data exploration such as simple observations for range of
# release years, dimensions, and column names
dim(Movies.df)
range(Movies.df$thtr_rel_year)
t(t(names(Movies.df)))
```

```{r}
# Do some correlation outlook using scatter plot matrix
ggpairs(Movies.df[, c('audience_score', 'imdb_rating', 'critics_score',
                      'runtime')])

# Look at correlation between MPAA rating and Audience score
ggplot(Movies.df, aes(x = mpaa_rating, y = audience_score)) + 
  geom_boxplot()
```


## Target Problem

Is there a correlation between the critic score and audience
score? Or genre and the audience score? How about MPAA rating and audience
score? My target problem is to find what variables affect the audience score
and whether we can predict the audience score using the variables such as
genre, critic rating, IMBD rating, release date, and runtime.

## Statistical Problem

My statistical problem will using the given variables such
as genre, MPAA rating, release dates, IMBD rating, and critic scores to predict
the audience score.

## Proposed Statistical Analysis

My proposed statistical analysis will be using a linear
regression model to predict the audience score of the movies. Some initial research
shows that there can be minimal correlation between certain variables to the
audience score such as movie runtime.


